A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-03-20 controlled_study.tex
+G1
use approx

\ifCLASSINFOpdf
  \usepackage{listings}
  \usepackage[pdftex]{graphicx}
  \usepackage{url}
  % \usepackage{caption}
  \usepackage{subcaption}
  \usepackage{tikz,pgfplots,pgfplotstable}
  \usepgfplotslibrary{statistics}
\else
\fi
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{itemize}
  \item Total installations: ~248K installs of the plug-in.
  \item Average daily installations: ~500.
\end{itemize}

@@

\textbf{Observation 4.} We observed the participants had problem completing API tasks that require multiple API calls without usage examples. Tasks T2 and T6 required the use of multiple API calls to complete successfully. Both tasks require an initial API call to find data using the API that is needed make a second API call. For example, P1.5 mentioned the following about T6, \textbf{``The post I created is not visible and not editable, though I got 201. Not sure why''}. After analyzing the response, we observed that P1.5 was able to create a blog post, but failed to publish it because it didn't have the $publish$ status. As a result, the post was not returned via the API for T6. P2.2 mentioned the following about T2: \textbf{``In case of search posts by author, it's not clear how to find the author\_id. Although, I realized that users and authors are same in this case.''}

>>>>

\ifCLASSINFOpdf
  \usepackage{listings}
  \usepackage[pdftex]{graphicx}
  \usepackage{url}
  % \usepackage{caption}
  \usepackage{subcaption}
  \usepackage{tikz,pgfplots,pgfplotstable}
  \usepackage{mathtools}
  \usepgfplotslibrary{statistics}
\else
\fi
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{itemize}
  \item Total installations: $ \approx 248K$ installs of the plug-in.
  \item Average daily installations: $ \approx 500$.
\end{itemize}

@@

\textbf{Observation 4.} We observed the G1 participants had problem completing API tasks that require multiple API calls without usage examples. Tasks T2 and T6 required the use of multiple API calls to complete successfully. Both tasks require an initial API call to find data using the API that is needed make a second API call. For example, P1.5 mentioned the following about T6, \textbf{``The post I created is not visible and not editable, though I got 201. Not sure why''}. After analyzing the response, we observed that P1.5 was able to create a blog post, but failed to publish it because it didn't have the $publish$ status. As a result, the post was not returned via the API for T6. P2.2 mentioned the following about T2: \textbf{``In case of search posts by author, it's not clear how to find the author\_id. Although, I realized that users and authors are same in this case.''}
